% acknowledgement.tex
\begin{center}
\section*{Acknowledgment}
\end{center}
\addcontentsline{toc}{section}{Acknowledgment}
I would like to express my heartfelt gratitude to the individuals who have contributed to the successful completion of the case study on Instrumentation II, focusing on the Gorkha Eco Red Bricks process.
\vspace{0.4cm} \\
First and foremost, I extend my sincere thanks to Er. Dinesh Gothe, Head of the Department, for his invaluable guidance, unwavering support, and insightful inputs throughout this case study. Your expertise and encouragement have been instrumental in shaping our understanding of the subject matter.
I am also deeply appreciative of the efforts and dedication shown by Ms. Ekata Niraula, our esteemed lecturer. Your thorough explanations, thought-provoking discussions, and willingness to address our queries have been pivotal in enriching our knowledge and driving this case study towards excellence.
I extend a special note of appreciation to Mr. Mesun Lakhemaru, our field supervisor, whose practical insights and real-world experience have provided us with a comprehensive understanding of the Gorkha Red Bricks process. Your willingness to share your expertise and guide us through practical intricacies is genuinely commendable.
\vspace{0.4cm} \\
I would like to express my gratitude to the entire academic community for fostering an environment of learning and exploration. Your collective efforts have played a significant role in our academic growth.
Lastly, I would like to acknowledge the support of my fellow classmates and colleagues who have shared ideas, experiences, and resources, contributing to the overall quality of this case study.
